Inpainting with controlled dimensionality reduction in the Fourier domain

### 2011-06-20 project/Paper/paper.tex
Minor, for pulling
Added parameter table

\begin{table*}
  \centering
  \begin{tabular}{|l|p{5cm}|p{5cm}|}
    \hline
    Function&Advantages&Disadvantages\\
    \hline
    $\exp(E)+\exp(T)$ & Increases cost fast to avoid $E$ or $T$ over a certain threshold & Not enough gradient for very low $E$, $T$ values\\
    \hline
    $(1-\exp(E))*(1-\exp(T))$ & Makes it possible to have large times for very low errors & Works also the other way around, and optimization only minimizes time\\
    \hline
    $E + T$ & Everywhere a good gradient & Time from 60 to 59 seconds is same \textit{improvement} as time from 2 to 1 second\\
    \hline
    $\begin{cases}
  \exp(E)  & \text{if }T<60\\
  \exp(E)+\exp(T/60 - 1) - 1 & \text{else}
\end{cases}$ & Optimizes for error only when time is low enough. Function still continous, penalizes high times. & None so far, this is the function used by us\\
    \hline
  \end{tabular}
  \caption{Different combined error functions}
  \label{error_function_table}
\end{table*}

@@

 We tested our algorithm and the two baselines on a set of natural images and further on a set of artificially created ones. (((TODO More than 1)))

@@

>>>>

\begin{table*}
  \centering
  \begin{tabular}{|l|p{5cm}|p{5cm}|}
    \hline
    Function&Advantages&Disadvantages\\
    \hline
    $\exp(E)+\exp(T)$ & Increases cost fast to avoid $E$ or $T$ over a certain threshold & Not enough gradient for very low $E$, $T$ values\\
    \hline
    $(1-\exp(E))*(1-\exp(T))$ & Makes it possible to have large times for very low errors & Works also the other way around, and optimization only minimizes time\\
    \hline
    $E + T$ & Everywhere a good gradient & Time from 60 to 59 seconds is same \textit{improvement} as time from 2 to 1 second\\
    \hline
    $\begin{cases}
  \exp(E)  & \text{if }T<60\\
  \exp(E)+\exp(T/60 - 1) - 1 & \text{else}
\end{cases}$ & Optimizes for error only when time is low enough. Function still continuous, penalizes high times. & None so far, this is the function used by us\\
    \hline
  \end{tabular}
  \caption{Different combined error functions}
  \label{error_function_table}
\end{table*}

@@

We tested our algorithm and the two baselines on a set of natural images and further on a set of artificially created ones. 
For evaluation, we tested these algorithms with different levels of missing pixels from 0 to 100\% in 5\% steps.

@@

\begin{table*}[p]
\begin{center}
\begin{tabular}{|c||c|c|c|}
\hline
Parameter & Meaning & Initial value & Optimized value\\
\hline\hline 
gauss\_size & Size of the gaussian & ? & ? \\
gauss\_sigma & Sigma of the gaussian & ? & ? \\
patch\_size & Patch size & ? & ? \\
patch\_frame\_size & Frame size & ? & ? \\
td\_abortbelow\_stdev & Minimal standard deviation for threshold determination& ? & ? \\
td\_abortbelow\_stepsize & Minimal step size for threshold determination & ? & ? \\
td\_middle &  Initial threshold & ? & ? \\
validation &  Size of the the validation set & ? & ? \\
max\_iterations & Maximum number of iterations & ? & ? \\
abortbelow\_change & Minimal change to perform another iteration & ? & ? \\

\hline
\end{tabular}
\end{center}
\caption{Parameters, their initial and optimized values}
\label{parameter_table}
\end{table*}%
